A Higher-Order Approach to Explicit Contexts in LF

### 2015-03-08 paper/paper.tex
Add references, close #1

\begin{abstract}
  There are two standard techniques for representing dependently typed calculi
  in the LF. The first is to re-use the LF contexts for the object contexts,
  which can lead to difficulties when the meaning of hypothetico-general
  judgement in the object language is stronger than in the LF; this is, for
  instance, the case in MLTT~1979, where non-trivial functionality obligations
  are incurred in the sequent judgement.

@@

To motivate this work, let us consider an encoding of MLTT~1979 in the logical
framework. The syntax contains two sorts, $\sortval$ (for canonical forms) and
$\sortexp$ (for non-canonical forms), and is defined in the following LF
signature: \footnote{LF signatures are presented in the style of inference
  rules for clarity. Object judgement forms have a \emph{mode} which expresses
  which arguments represent inputs, and which represent outputs; in our
  presentation, we color the inputs \emph{\InputMode\InputModeColorName}, and
  the outputs \emph{\OutputMode\OutputModeColorName}. Proper assignment of
modes may be used to construe a judgement as having algorithmic content.}

@@

>>>>

\begin{abstract}

  There are two standard techniques for representing dependently typed calculi
  in the LF. The first is to re-use the LF contexts for the object contexts,
  which can lead to difficulties when the meaning of hypothetico-general
  judgement in the object language is stronger than in the LF; this is, for
  instance, the case in MLTT~1979, where non-trivial functionality obligations
  are incurred in the sequent judgement.

@@

To motivate this work, let us consider an encoding of Martin-L\"of's
extensional, polymorphic type theory (MLTT~1979) in the logical framework (see
\cite{Martin-Lof-1979} for a full presentation). The syntax contains two sorts,
$\sortval$ (for canonical forms) and $\sortexp$ (for non-canonical forms), and
is defined in the following LF signature: \footnote{LF signatures are presented
  in the style of inference rules for clarity. Object judgement forms have a
  \emph{mode} which expresses which arguments represent inputs, and which
  represent outputs; in our presentation, we color the inputs
  \emph{\InputMode\InputModeColorName}, and the outputs
  \emph{\OutputMode\OutputModeColorName}. Proper assignment of modes may be
used to construe a judgement as having algorithmic content.}

@@

\bibliographystyle{acmtrans}
\nocite{*}
\bibliography{paper}
